experiment 1

### 2021-09-16 experiments/experiment 1/experiment-1.Rmd
Conversion next step

library(microxanox)
if (packageVersion("microxanox") < package_version("0.2.3")) {
  stop("microxanox version needs to be at least 0.2.3!")
}
library(tidyverse)
library(patchwork)
library(here)
source(here("experiments/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
#options(mc.cores = 8)
eval_dynamics_flag <- FALSE
```

@@

parameter <- new_runsim_parameter(
  dynamic_model = bushplus_dynamic_model,
  event_definition = event_definition_1,
  event_interval = 100,
  noise_sigma = 0,
  minimum_abundances = rep(0, 3),
  sim_duration = 2000,
  sim_sample_interval = 100,
  strain_parameter = sp,
  log10a_series = c(
    log10(sp$a_O),
    log10(sp$a_O)
  )
)
names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
rm(sp)

@@

```{r eval = eval_dynamics_flag}
stop("CHECK PARAMETER VALUES")
# default_log10a_series <- c(-1, -7, -7)
parameter$log10a_series <- c(-1, -7, -7)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/num_CB_strains
sim_res_novar1 <- run_simulation(parameter)
saveRDS(sim_res_novar1, here("experiments/experiment 1/data/sim_res_novar1.RDS"))
```

@@

```{r eval = eval_dynamics_flag}
sim_number <- num_div_treatment_levels
sim_res_highvar1 <- run_simulation(parameter_values = var_expt$pars[[max_diversty_all]],
                          initial_state = initial_state)
saveRDS(sim_res_highvar1, here("experiments/experiment 1/data/sim_res_highvar1.RDS"))
```

@@

```{r eval = eval_dynamics_flag}
default_sim_duration <- 60000
```

```{r eval = eval_dynamics_flag}
sim_number <- 1
default_log10a_series <- c(-5, -3, -1, -1)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
sim_res_novar2 <- run_simulation(parameter_values = var_expt$pars[[no_diversity]],
                          initial_state = initial_state)
saveRDS(sim_res_novar2, here("experiments/experiment 1/data/sim_res_novar2.RDS"))
```

@@

```{r eval = eval_dynamics_flag}
sim_number <- num_div_treatment_levels
sim_res_highvar2 <- run_simulation(parameter_values = var_expt$pars[[max_diversty_all]],
                          initial_state = initial_state)
saveRDS(sim_res_highvar2, here("experiments/experiment 1/data/sim_res_highvar2.RDS"))
```

@@

```{r eval = eval_dynamics_flag}
default_sim_duration <- 1000000
```

```{r eval = eval_dynamics_flag}
default_minimum_abundances <- rep(100, 3)
names(default_minimum_abundances) <- c("CB", "PB", "SB")
```

```{r eval = eval_dynamics_flag}
sim_number1 <- 1
default_log10a_series <- c(-1, -8, -1)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
sim_res_novar3 <- run_simulation(parameter_values = var_expt$pars[[no_diversity]],
                          initial_state = initial_state)
saveRDS(sim_res_novar3, here("experiments/experiment 1/data/sim_res_novar3.RDS"))
```

>>>>

library(microxanoxBeta)
if (packageVersion("microxanoxBeta") < package_version("0.2.3")) {
  stop("microxanox version needs to be at least 0.2.3!")
}
library(tidyverse)
library(patchwork)
library(here)
source(here("experiments/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
#options(mc.cores = 8)
eval_dynamics_flag <- FALSE
```

@@

parameter <- new_runsim_parameter(
  dynamic_model = bushplus_dynamic_model,
  event_definition = event_definition_1,
  event_interval = 100,
  noise_sigma = 0,
  minimum_abundances = rep(1, 3),
  sim_duration = 2000,
  sim_sample_interval = 100,
  strain_parameter = sp,
  log10a_series = c(
    log10(sp$a_O),
    log10(sp$a_O)
  )
)
names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
rm(sp)

@@

```{r eval = eval_dynamics_flag}
# default_log10a_series <- c(-1, -7, -7)
parameter$log10a_series <- c(-1, -7, -7)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/num_CB_strains
# sim_res_novar1 <- run_simulation(parameter)
# saveRDS(sim_res_novar1, here("experiments/experiment 1/data/sim_res_novar1.RDS"))
```

@@

```{r eval = eval_dynamics_flag}
# Is this actually needed?
# sim_number <- num_div_treatment_levels

parameter$strain_parameter <- var_expt$pars[[max_diversty_all]]
parameter$strain_parameter$initial_state <- sim_res_novar1$strain_parameter$initial_state
sim_res_highvar1 <- run_simulation(parameter)
saveRDS(sim_res_highvar1, here("experiments/experiment 1/data/sim_res_highvar1.RDS"))
```

@@

```{r eval = eval_dynamics_flag}
parameter$sim_duration <- 60000
```

```{r eval = eval_dynamics_flag}
# sim_number <- 1
parameter$log10a_series <- c(-5, -3, -1, -1)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
sim_res_novar2 <- run_simulation(parameter)
saveRDS(sim_res_novar2, here("experiments/experiment 1/data/sim_res_novar2.RDS"))
```

@@

```{r eval = eval_dynamics_flag}
sim_number <- num_div_treatment_levels
parameter$strain_parameter <- var_expt$pars[[max_diversty_all]]
parameter$strain_parameter$initial_state <- sim_res_novar2$strain_parameter$initial_state
sim_res_highvar2 <- run_simulation(parameter)
saveRDS(sim_res_highvar2, here("experiments/experiment 1/data/sim_res_highvar2.RDS"))
```

@@

```{r eval = eval_dynamics_flag}
parameter$sim_duration <- 1000000
```

```{r eval = eval_dynamics_flag}
parameter$minimum_abundances <- rep(100, 3)
names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
```

```{r eval = eval_dynamics_flag}
# sim_number1 <- 1
stop("CONTINUE HERE!!!!!")
parameter$log10a_series <- c(-1, -8, -1)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10/num_CB_strains
sim_res_novar3 <- run_simulation(parameter)
saveRDS(sim_res_novar3, here("experiments/experiment 1/data/sim_res_novar3.RDS"))
```
